A Partitioning Algorithm for Maximum Common (Connected) Subgraphs\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/K503058/1 and EP/M508056/1]}

### 2017-02-04 paper/paper.tex
More plotting

Dual Xeon E5-2640 v2 CPUs, 64GBytes RAM. Parallel experiments 16 threads (one per hardware core), and 32 with hyper-threading.

@@

\paragraph{Large subgraph isomorphism instances} have yet to be run.

\paragraph{Compared to CP FC} Runtimes are in \cref{figure:plain-james-versus-cp-fc-scatter} and \cref{figure:33ved-james-versus-cp-fc-scatter}, and nodes are in \cref{figure:plain-james-versus-cp-fc-nodes-scatter} and \cref{figure:33ved-james-versus-cp-fc-nodes-scatter}.

@@

\begin{figure}
    \centering
    \includegraphics*{gen-graph-plain-james-versus-cp-fc-scatter.pdf}
    \caption{MCS Plain instances, James vs CP-FC, Runtimes (TODO?? heatmapify this)}\label{figure:plain-james-versus-cp-fc-scatter}
\end{figure}

\begin{figure}
    \centering
    \includegraphics*{gen-graph-33ved-james-versus-cp-fc-scatter.pdf}
    \caption{MCS 33\% vertex and edge labelled directed instances, James vs CP-FC, Runtimes (TODO?? heatmapify this)}\label{figure:33ved-james-versus-cp-fc-scatter}
\end{figure}

\begin{figure}
    \centering
    \includegraphics*{gen-graph-plain-james-versus-cp-fc-nodes-scatter.pdf}
    \caption{MCS Plain instances, James vs CP-FC, Nodes (TODO?? heatmapify this)}\label{figure:plain-james-versus-cp-fc-nodes-scatter}
\end{figure}

\begin{figure}
    \centering
    \includegraphics*{gen-graph-33ved-james-versus-cp-fc-nodes-scatter.pdf}
    \caption{MCS 33\% vertex and edge labelled directed instances, James vs CP-FC, Nodes (TODO?? heatmapify this)}\label{figure:33ved-james-versus-cp-fc-nodes-scatter}
\end{figure}

>>>>

Dual Xeon E5-2640 v2 CPUs, 64GBytes RAM. Parallel experiments 32 threads, using
all 16 physical cores with hyper-threading enabled.

@@

\paragraph{Large subgraph isomorphism instances} are in \cref{figure:sip-cumulative}.

\paragraph{Compared to CP FC} Nodes are in \cref{figure:plain-james-versus-cp-fc-nodes-scatter} and \cref{figure:33ved-james-versus-cp-fc-nodes-scatter}.

\paragraph{Nodes compared to kdown on SIP} have yet to be run.

@@

\begin{figure}
    \centering
    \includegraphics*{gen-graph-sip-cumulative.pdf}
    \caption{SIP instances, cumulative runtimes}\label{figure:sip-cumulative}
\end{figure}

\begin{figure}
    \centering
    \includegraphics*{gen-graph-plain-james-versus-cp-fc-nodes-scatter.pdf}
    \caption{MCS Plain instances, James vs CP-FC, Nodes (TODO?? heatmapify this
    and exclude timeouts)}\label{figure:plain-james-versus-cp-fc-nodes-scatter}
\end{figure}

\begin{figure}
    \centering
    \includegraphics*{gen-graph-33ved-james-versus-cp-fc-nodes-scatter.pdf}
    \caption{MCS 33\% vertex and edge labelled directed instances, James vs
    CP-FC, Nodes (TODO?? heatmapify this and exclude
    timeouts)}\label{figure:33ved-james-versus-cp-fc-nodes-scatter}
\end{figure}
